---
title: "The Office IMDB Ratings"
author: "Pete Talbert"
date: "8/20/2020"
output: word_document
---

```{r, your turn instructions, include=FALSE}
# Let's practice knitr options! -----------------------------------
# 1) IN THE FIRST R SETUP CHUNK BELOW, CHANGE echo TO TRUE, AND RE-KNIT. HOW IS THE OUTPUT DIFFERENT?
# 2) CHANGE echo BACK TO FALSE; NOW CHANGE BOTH warning AND message TO TRUE, AND RE-KNIT. HOW IS THE OUTPUT DIFFERENT?
# 3) CHANGE warning AND message BACK TO FALSE; IN THE SECOND CHUNK WHERE WE IMPORT THE DATA, INSIDE THE CURLY BRACES TYPE eval = FALSE, AND RE-KNIT. 
# WHAT ERROR DID IT GIVE YOU AND WHY?
# 4) REMOVE eval = FALSE, AND NOW PUT THE FOLLOWING IN THE SAME CODE CHUNK: fig.width = 4, fig.height = 4, dpi = 700, AND RE-KNIT. 
# WHAT DO THESE SETTINGS DO?
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Do average IMDB ratings for The Office change across seasons?

*The Office* saw higher average IMDB ratings of its episodes the first seven seasons, but in seasons eight and nine it dipped.

```{r}
library(tidyverse)

office_ratings <- read_csv("data/office_ratings.csv")

office_ratings %>% 
  group_by(season) %>% 
  summarize(avg_imdb_rating = mean(imdb_rating)) %>% 
  mutate(season = as_factor(season)) %>% 
  ggplot(aes(x = season, y = avg_imdb_rating)) +
  geom_col()
```

However, in season nine, the finale was one of the highest rated episodes of the entire series.

```{r}
office_ratings %>% 
  filter(season == 9) %>% 
  ggplot(aes(x = episode, y = imdb_rating, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 10))
```

### About the data

The data are IMDB ratings for each episode of *The Office*, the hit NBC show that ran in the mid-2000s. The data comes from the Tidy Tuesday R project, and can be found [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-03-17). Overall, there were `r count(office_ratings)` rows in the data.

