---
title: "The Office IMDB Ratings"
author: "Pete Talbert"
date: "8/20/2020"
output: 
  word_document:
    reference_docx: "../../templates/word-styles-office-2016.docx"
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)

office_ratings <- read_csv("data/office_ratings.csv")

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 700)
ggplot2::theme_set(ggplot2::theme_minimal())
```

## Introduction

Below we see the overall number of epsiodes per season and the average IMDB ratings. Clearly, the show declined in popularity across time.

```{r}
office_ratings %>% 
  group_by(season) %>% 
  summarize(avg_imdb_rating = mean(imdb_rating),
            n_of_episodes = n()) %>% 
  kable(caption = "Summary of The Office seasons", digits = 1, col.names = c("Season", "Average IMDB Rating", "No. of Episodes"))
```


## Do average IMDB ratings for The Office change across seasons?

*The Office* saw higher average IMDB ratings of its episodes the first seven seasons, but in seasons eight and nine it dipped.

```{r}
office_ratings %>% 
  group_by(season) %>% 
  summarize(avg_imdb_rating = mean(imdb_rating)) %>% 
  mutate(season = as_factor(season)) %>% 
  ggplot(aes(x = season, y = avg_imdb_rating)) +
  geom_col()
```

However, in season nine, the finale was one of the highest rated episodes of the entire series.

```{r}
office_ratings %>% 
  filter(season == 9) %>% 
  ggplot(aes(x = episode, y = imdb_rating, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 10))
```

### About the data

The data are IMDB ratings for each episode of *The Office*, the hit NBC show that ran in the mid-2000s. The data comes from the Tidy Tuesday R project, and can be found [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-03-17). Overall, there were `r count(office_ratings)` rows in the data.

