---
title: "The Office IMDB Ratings"
author: "Pete Talbert"
date: "8/20/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)

tuition_cost <- read_csv("data/tuition_cost.csv")

diversity_school <- read_csv("data/diversity_school.csv")

salary_potential <- read_csv("data/salary_potential.csv")
```

```{r, your turn instructions, include=FALSE}
# Let's practice skimming our new datasets! -----------------------------------
# 1) IN THE # 1) CODE CHUNK BELOW, RUN THE skim() FUNCTION ON THE diversity_school AND salary_potential DATASETS. DON'T FORGET TO LOAD THE PACKAGE!
# 2) USING JUST PLAIN TEXT, ANSWER THE QUESTIONS UNDER THE #2) HEADER. USE THE MARKDOWN SYNTAX TO MAKE AN UNORDERED LIST AND/OR USE INLINE R CODE OR
#    USE A CODE CHUNK TO FIND THESE ANSWERS WITH CODE!
```

# 1)

```{r}
# install.packages("skimr")
library(skimr)

skim(diversity_school)
skim(salary_potential)

# You may want to reference some values in the skim output, so I've saved these as objects.
skim_diversity <- skim(diversity_school)
skim_salary <- skim(salary_potential)
```

# 2)

## How many rows and columns are in `diversity_school`? `salary_potential`?

* `diversity_school` has `r count(diversity_school)` rows and `r length(diversity_school)` columns
* `salary_potential` has `r count(salary_potential)` rows and `r length(salary_potential)` columns

## How many unique demographic values are there in the `category` column of `diversity_school`? What are they?

* 11 unique values.
* `r diversity_school %>% distinct(category)`

## What columns have missing values in `diversity_school` and `salary_potential`? What are the completion rates of each column (i.e., what % of values are non-missing)?

```{r}
skim_diversity %>% 
  filter(n_missing > 0) %>% 
  select(skim_variable, n_missing, complete_rate)

skim_salary %>% 
  filter(n_missing > 0) %>% 
  select(skim_variable, n_missing, complete_rate)
```


