---
title: "Module 6 Your Turns"
author: "Pete Talbert"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)

tuition_cost <- read_csv("data/tuition_cost.csv")

diversity_school <- read_csv("data/diversity_school.csv")

salary_potential <- read_csv("data/salary_potential.csv")
```

```{r, your turn instructions, include=FALSE}
# Let's practice dealing with duplicates! -----------------------------------
# 1) FROM diversity_school PIPE IN AN add_count() WITH NO COLUMNS (JUST AN EMPTY FUNCTION). WHAT DOES IT RETURN?
#    NOW ADD THE state COLUMN INSIDE add_count(). HOW DID THE n COLUMN CHANGE?
# 2) ADD BOTH state AND name INSIDE add_count(). WHY DOES IT SHOW 11 FOR EACH ROW?
# 3) NOW LET'S USE distinct(). START BY JUST PIPING IN A distinct() WITH NO COLUMNS (JUST AN EMPTY FUNCTION). WHAT DOES IT RETURN?
#    NOW ADD THE name COLUMN INSIDE distinct(). HOW DID THE TOTAL NUMBER OF ROWS CHANGE? HOW MANY DISTINCT UNIVERSITIES ARE IN THE DATASET?
#    NOW ADD THE name, total_enrollment, AND state INSIDE distinct(). WHY IS THE TOTAL NUMBER OF ROWS MORE THAN THE PREVIOUS COUNT WHERE WE ONLY HAD name?
```

# 1)

```{r}
diversity_school %>% 
  add_count()

diversity_school %>% 
  add_count(state)
```

* When we pipe an empty `add_count()`, we get a column, `n`, that lists a count of the total number of rows in the dataframe: 50,655.
* When we place `state` inside `add_count()`, we get the count of rows for each state. Arizona, for instance, has 956 rows in the data.

# 2)

```{r}
diversity_school %>% 
  add_count(state, name)
```

It shows 11 because, each university has 11 rows, one for each demographic category.

# 3)

```{r}
diversity_school %>% 
  distinct()

diversity_school %>% 
  distinct(name)

diversity_school %>% 
  distinct(name, total_enrollment, state)
```

* Putting `name` only in the `distinct()` function returned 4,575 distinct universities.
* Putting `name`, `total_enrollment`, and `state` in the `distinct()` function returned 4,604 distinct universities. This is because we have those NA rows where there appears to be enrollment counts, but no name, or state. This was a good check that we definitely want to filter out those NA rows before we work with a distinct dataframe of univerisities with their state and total enrollment.
